An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-10 EconGrowth2.Rnw
Added CES prediction graphs for (le)k and (ek)l nestings.

<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.", eval=FALSE>>=
createCESLatticeGraph()
@

>>>>

<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
createCESLatticeGraph(nest="(kl)e")
@

Figure~\ref{fig:CES_GDP_Lattice_Graph_lek} compares CES model predictions 
to historical data for the $(le)k$ nesting.

<<CES_GDP_Lattice_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($le$)$k$ nesting.">>=
createCESLatticeGraph(nest="(le)k")
@

Figure~\ref{fig:CES_GDP_Lattice_Graph_ekl} compares CES model predictions 
to historical data for the $(ek)l$ nesting.

<<CES_GDP_Lattice_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($ek$)$l$ nesting.">>=
createCESLatticeGraph(nest="(ek)l")
@
